\Frame {Conclusion}
{
\I We are concerned with effective and estimation of MIMO mm-wave channel by exploiting its sparsity, and studied Dantzig Selector (DS).

\I We modified DS for present setting: for the almost-sparse condition, for the angular domain, for the beamformer matrix \m {\M {P}} in our setting, and for complex vectors.

\I We bound the expected square error and the successful probability, in explicit expression of system parameters such as \m {N_H}, \m {N_Y}, and \m{L}.
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {Future Work}
{
\I Check the proof again, especially the approximation decision.

\I Simulate many different parameters such as \m {N_H}, \m {N_Y}, and \m{L} and discuss extensively.

\I Verify (if correct) the successful-probability bound and observe how \m {N_Y, N_H} affects it (if any).

\I Also implement (some or all of) OMP, LS, LASSO among others, and compare them.
}
% % % % % % % % % % % % % % % % % % % % % % % % % %
\Frame {References}
{
{\tfx
\I D Achlioptas (2001). Database-friendly random projections. In Proceedings of the twentieth ACM SIGMOD-SIGACT-SIGART symposium on Principles of database systems (pp. 274-281). ACM.

\I W U Bajwa, J Haupt, G Raz, and R Nowak (2008), ``Compressed Channel Sensing'', 2008 42nd Annual Conference on Information Sciences and Systems.

\I R Baraniuk, M Davenport, R DeVore, and M Wakin (2008), ``A Simple Proof of the Restricted Isometry Property for Random Matrices'', \It{Constructive Approximation} \Bf{28}: 253–263

\I E J Cand\`es and T Tao (2005), ``Decoding by Linear Programming'', \It{IEEE Transactions on Information Theory}, Vol.51, No.12.

\I E Cand\`es and T Tao (2007), ``The Dantzig Selector: Statistical Estimation when \m {p} is Much Larger than \m {n}'', \It{The Annals of Statistics}, Vol.35, No.6.
}
}

