\Frame {Conclusion}
{
\I We estimate MIMO mm wave channel \m {\M {H}} by using a modified DS.

\I We justify DS under relaxed sparsity of \m {\V {g}}, and demonstrate the RIP of effective beamformer \m {\M {P}}.

\I We analyze the error norm of DS in terms of \m {N_H}, \m {N_{B,t}}, \m {N_{B,r}}, and \m{L}, and approximate the asymptotic failure probability.

\I We suggest several ways of reducing the complexity, and illustrate in simulation that DS often outperforms other methods.

\I We suspect that in cases of higher noise, less sample, or less sparsity, DS is more suitable, so it may be used in combination to other methods.
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References (1/2)}
{
{\tfx
\I A Alkhateeb, G Leus, and R W Heath, \Quote {Compressed sensing based multi-user millimeter wave systems: How many measurements are needed?}, in \It {2015 IEEE International Conference on Acoustics, Speech and Signal Processing}.

\I W U Bajwa, J Haupt, A M Sayeed, and R Nowak, \Quote {Compressed channel sensing: A new approach to estimating sparse multipath channels}, \It {Proceedings of the IEEE}, 2010

\I S Boyd and L Vandenberghe, \It {Convex optimization}, Cambridge U Press, 2004.

\I E Candès and T Tao, \Quote {The Dantzig Selector: Statistical estimation when \It {p} is much larger than \It {n}}, \It {The Annals of Statistics}, 2007.
}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {References (2/2)}
{
{\tfx
\I G Destino, M Juntti, and S Nagaraj (2015): \Quote {Leveraging sparsity into massive MIMO channel estimation with the adaptive-LASSO}, in \It {IEEE Global Conference on Signal and Information Processing}

\I J Lee, G-T Gil, and Y H Lee, \Quote {Channel estimation via orthogonal matching pursuit for hybrid MIMO systems in millimeter wave communications}, \It {IEEE Transactions on Communications}, 2016.

\I J A Tropp and A C Gilbert, \Quote {Signal recovery from random measurements via orthogonal matching pursuit}, \It {IEEE Transactions on information theory}, 2007.

\I E Vlachos, G C Alexandropoulos, and J Thompson (2019): \Quote {Wideband MIMO channel estimation for hybrid beamforming millimeter wave systems via random spatial sampling}, \It {IEEE Journal of Selected Topics in Signal Processing}, 2019
}
}


% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %

% graph mark should be "SNR"
% Ben-Haim et al thinks DS better in high SNR, why?
% Find 5G usage of low SNR sceneario
% explain higher complexity of DS in high SNR
% input data stream dimension should equal output
% case that $H$ is not square
% case that $N_{R,t}=2*N_{B,t}$
% in Chap 3, argue instead that various compressive sensing can be used


